----------------------------------------------------------------------------------
title: "Getting and cleaning data project"
author: "Lorena Vilela"
date: "26 September 2015"
output: html_document
-----------------------------------------------------------------------------------
<br>Tidy dataset results from the script run_analysis.R:

Average Measures per Activity per Subject

```{r}
measures <- read.table("../project/activity_measures.txt", header = TRUE)
summary(measures)
```

Activity

```{r}
activity <- read.table("../project/activity.txt", header = TRUE)
summary(activity)
```

List of steps performed to create the dataset as above. 

Step 1- Collect data about Human Activity Recognition Using Smartphones Dataset available in  https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip

Step 2- Merging train and test data to create one data set.
Step 2.1 - Merge train data into variable dt_train
Step 2.2 - Merge test data into variable dt_test
Step 2.3  - Merge train and test data into variable dt and name all the columns from col1 to col563

Step 3-Extracts only the measurements on the mean and standard deviation for each measurement. 
<br>Step 3.1-Read the features lables into the variable dt_features
<br>Step 3.2-Search only the mean and std features positions
<br>Step 3.3-Record only the mean and std features into dt_std_mean

Step 4-Uses descriptive activity names to name the activities in the data set
<br>Step 4.1 Read the acitivity lables into the variable dt_activities and setup the column names as col1 and col2
<br>Step 4.2 Merge the activity labels to the train and test data into dt

Step 5-Appropriately labels the data set with descriptive variable names according to the order into the variable dt - first activity id, features names, subject and activity label

Step 6-Creates a second, independent tidy data set with the average 
    ##of each variable for each activity and each subject.
<br>Step 6.1- Applying the principle of tidy data- Each variable forms a column and each observation forms a row.
<br>Step 6.1.1- First melt data because the features are columns instead of rows and they are a mixed of variables.
<br>Step 6.2- Calculate the average measure by activity and subject
<br>Step 6.3 - Applying the 3rd principle of tidy data - Each type of observational unit forms a table
<br>Step 6.3.1 - Create the Activity table and  the Average measures by activities and subject table - see the dataset in the begining of this document.



