----------------------------------------------------------------------------------
title: "Getting and cleaning data project"
author: "Lorena Vilela"
date: "26 September 2015"
output: html_document
-----------------------------------------------------------------------------------

Tidy dataset results from the script run_analysis.R:

Average Measures of features by Activity and Subject

```{r}
tidy_data <- read.table("../project/tidy_data.txt", header = TRUE)
summary(tidy_data)
```

List of steps performed to create the dataset above:

Step 1- Collect data about Human Activity Recognition Using Smartphones available in  https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip

Step 2- Merging train and test data to create one data set.<br>
Step 2.1 - Merge train data into variable dt_train.<br>
Step 2.2 - Merge test data into variable dt_test.<br>
Step 2.3  - Merge train and test data into variable dt and name all the columns from col1 to col563.<br>

Step 3-Extracts only the measurements on the mean and standard deviation for each measurement.<br>
Step 3.1-Read the features lables and record into the variable dt_features.<br>
Step 3.2-Record the subject, activity and the mean and std measurements into dt_std_mean.<br>

Step 4-Uses descriptive activity names to name the activities in the data set.<br>
Step 4.1 Read the acitivity lables into the variable dt_activities and setup the column names as col1 and col2.<br>
Step 4.2 Merge the activity labels to the dt_std_mean (data result from step 3.2).<br>

Step 5-Appropriately labels the data set with descriptive variable names according to the order into the variable dt_std_mean (data result from step 4.2)

Step 6-Create an independent tidy data set with the average of each feature - extracted according to step 3 - by activity and subject.<br>
Step 6.1- Applying the principle of tidy data - Each variable forms a column and each observation forms a row.<br>
Step 6.1.1- First melt the data because the features are columns instead of rows and they are a mixed of information.<br>
Step 6.2- Calculate the average measure of the features by activity and subject.<br>
Step 6.3- Adjust the column names.<br>
See the tidy data sample:<br>
```{r}
print(head(tidy_data, 5))
```


